---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spg

**NOTE: This is a toy package created for expository purposes**
<!-- badges: start -->
<!-- badges: end -->

The goal of spg is to demonstrate R skills in context of a vacature for RES at team MNM (INBO)

- Load data from shared google drive
- manipulate and aggregate data into required measure (sample_size = "steekproefgrootte")
- plot measure to compare datasets

## Installation

You can install the development version of spg from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("nick-dil/MNM-RES-demo")
```

## Example

> [!NOTE]
> See the `examples/00_tutorial.R`

This is a basic example which shows you how to solve the exercise:

```{r example, echo = FALSE}
library(spg)
library(tidyverse)

# Retrieve POC dir ids ~ version
poc_id_list = getPocIdList()

# Read and create aggregated sample size ~ dataset, see exercise
demo.v131 = readPocSampleData(poc_id_list$poc_0.13.1) %>% 
  makeSpgTable() %>% wrangleSpgTable()

demo.v140 = readPocSampleData(poc_id_list$poc_0.14.0) %>% 
  makeSpgTable() %>% wrangleSpgTable()

```

Inspect a dataset:

```{r demo14}
summary(demo.v140)
```

And compare the sample_size between datasets with some exploratory plots:

```{r pressure, echo = FALSE}

# Make comparison plots
demo_plots = plotSpgComparison(demo.v131, demo.v140)

demo_plots$spg_barplot
demo_plots$spg_diff_barplot
demo_plots$spg_scatter

```
